Gaussian mean estimation in simulated data sets

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

```{r extract-data-for-barplots-homo, fig.height=5, fig.width=8}
create.bar.plots(rbind(
  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
```

>>>>

```{r summarize-results-homo, fig.height=4, fig.width=8}
create.bar.plots(rbind(
  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
```
